Precision calculations for cosmic shear

### 2017-02-08 cfhtlens.tex
Some updates on the results section Purple text for MK to review

In this work, we focus on the weak-lensing power spectrum projection, and
assess the impact of various approximations on cosmological constraints from
CFHTLenS. We re-analyse the 2D CFHTLenS data from \cite{CFHTLenS-2pt-notomo},
adopting the same priors and non-linear power spectrum corrections\footnote{As
an example of significant effects that need to be accounted for using the
revised non-linear power spectrum of \cite{2012ApJ...761..152T} in place of
\cite{2003MNRAS.341.1311S} results in a decrease of $0.6 \sigma$ with $\sigma_8
(\Omega_{\rm m}/0.27)^{0.6} =0.768^{+0.029}_{-0.031}$.} from
\cite{2003MNRAS.341.1311S} as the original \cite{CFHTLenS-2pt-notomo} analysis.
For a first-order standard Limber flat-sky approximation (L1Fl) we find
$\sigma_8 (\Omega_{\rm m}/0.27)^{0.6} =0.787^{+0.031}_{-0.033}$. For a
second-order extended Limber flat-sky approximation we find $\sigma_8
(\Omega_{\rm m}/0.27)^{0.6} =X^{+X}_{-X}$, a negligible change of
$X\sigma$.

@@

\ch{This text taken from the comment on paper; We note that
\citet{2016arXiv161104954K} use their `Flat' approximation for their `Full'
non-Limber analysis of the CFHTLenS data.   This is because on a sphere,
correlation functions cannot be related to the power spectrum by a Hankel
transform (e.g. equation~\ref{eqn:xiGG}) as the power spectrum is not defined
for non-integer $\ell$. In Figure~\ref{fig:Cl_xi}, however, we show that this
chosen version of a flat-sky approximation serves to exacerbate the tension in
theoretical models when a flat-sky solution is compared with the spherical-sky
solution in the Limber approximated case.  This is not the case when
considering the standard $T_\ell = 1$ flat-sky approximation that has been used
in the majority of cosmic shear studies to date.  We would therefore argue that
it is more appropriate to use a $T_\ell = 1$ flat-sky approximation when
carrying out a `Full' non-Limber analysis of the shear correlation function
obtained from the Hankel transformation (equation~\ref{eqn:xiGG}). We need to
take a decision here about what to use.  Do we need a Full Flat case in Table
1, and to demonstrate that Ext2Fl is very close to FullFl?  And then use Ext2Fl
as our "truth" for the correlation function?}

>>>>

\ch{New stuff here - see if you approve - edit and then de-purple it!}

\ch{In this work, we focus on the weak-lensing power spectrum projection, and
assess the impact of various approximations on cosmological constraints from
CFHTLenS. We re-analyse the 2D CFHTLenS measurement of the two-point shear correlation function $\xi_\pm(\theta)$ from \cite{CFHTLenS-2pt-notomo}, which is
given by}
\begin{equation}
\xi_\pm^{ij}(\theta) = \frac{1}{2\pi}\int_0^\infty \d\ell \,\ell \,P^{ij}_\gamma(\ell) \, J_{0,4}(\ell \theta) \, , 
\label{eqn:xiGG}
\end{equation}
\ch{where $J_{0,4} (\ell \theta)$ is the zeroth (for $\xi_+$) or fourth (for $\xi_- $) order Bessel function of the first kind and $P_\gamma(\ell)$ is the shear power spectrum at angular wave number $\ell$ which can be related to the underlying matter power spectrum through equation~\ref{eq:P_ell_limber1} when adopting a first-order extended Limber approximation, or equation~\ref{eq:P_ell_limber2} when adopting a second-order extended Limber approximation \citep[for more details see][and references therein]{miraldaescude:1991, kaiser:1992, bartelmann/schneider:2001}.  Note that as we have shown in section~\ref{sec:comp} that the second-order extended Limber approximation provides a percent-level precision representation of the full spherical projection, we do not investigate predictions for the two-point shear correlation function using the full spherical projection.  This is because on a sphere,
correlation functions cannot be related to the power spectrum by a Hankel transform (e.g. equation~\ref{eqn:xiGG}) as the power spectrum is not defined for non-integer $\ell$.}

For consistency, we adopt the same priors and non-linear power spectrum corrections\footnote{As
an example of more significant effects that need to be accounted for, when using the
revised non-linear power spectrum of \cite{2012ApJ...761..152T} in place of
\cite{2003MNRAS.341.1311S}, there is a decrease of $0.6 \sigma$ with $\sigma_8
(\Omega_{\rm m}/0.27)^{0.6} =0.768^{+0.029}_{-0.031}$.} from
\cite{2003MNRAS.341.1311S} as the original \cite{CFHTLenS-2pt-notomo} analysis.
For a first-order standard Limber flat-sky approximation (L1Fl) we find
$\sigma_8 (\Omega_{\rm m}/0.27)^{0.6} =0.787^{+0.031}_{-0.033}$. For a
second-order extended Limber flat-sky approximation we find $\sigma_8
(\Omega_{\rm m}/0.27)^{0.6} =X^{+X}_{-X}$, a negligible change of
$X\sigma$.

@@
